Thesis: draft

### 2021-04-06 draft.tex
added more figures

\subsection{Evolution of opinions}
% write explanation here! Also mention all model parameters (eg Q=10, etc)!!
\begin{figure}[h!]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_001_50-50_PR_REC.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_50-50_PR_REC.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_10x100_01-0001_003-0008_50-50_PR_REC.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_10x100_10-001-0001_50-50_PR_REC.png}
    \caption{SBM-WS}
  \end{subfigure}
  \caption{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ distribution. Four different network models are used (each with an average degree around 10 and a total number of nodes equal to 1000): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS), $K = 10$, two slightly different values of the clustering coefficient are used ($\left<C\right> \sim 0.55$ and $\left<C\right> \sim 0.60$); \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100 ($10\times100$), a high modularity case ($p_{cl} = 0.1,\ p_{add} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{cl} = 0.03,\ p_{add} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100 ($10\times100$), each community has the following WS parameters: $K = 10,\ \beta = 0.01$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. For each model two different filtering algorithms are compared to each other: the REC and the PR filtering algorithm. Each figure is the result of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\end{figure}
\newpage
\subsection{Echo chambers}

>>>>

\subsection{Evolution of opinions}
\textbf{Starting conditions $\bm{P_0(0) = 0.5}$ and $\bm{P_1(0)=0.5}$}\\
\newline
 write explanation here! Also mention all model parameters (eg Q=10, etc)!!
\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_001_50-50_PR_REC.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_50-50_PR_REC.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_10x100_01-0001_003-0008_50-50_PR_REC.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_10x100_10-001-0001_50-50_PR_REC.png}
    \caption{SBM-WS}
  \end{subfigure}
  \caption{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ distribution. Four different network models are used (each with an average degree around 10 and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS), $K = 10$, two slightly different values of the clustering coefficient are used ($\left<C\right> \sim 0.55$ and $\left<C\right> \sim 0.60$); \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100 ($10\times100$), a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100 ($10\times100$), each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. For each model two different filtering algorithms are compared to each other: the REC and the PR filtering algorithm. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\end{figure}
\newpage
\noindent
\textbf{Starting conditions $\bm{P_0(0) = 0.2}$ and $\bm{P_1(0)=0.8}$}\\
\newline

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_001_50-50_PR_REC_20-80_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_10-006_PR_REC_20-80_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_10x100_01-0001_003-0008_50-50_PR_REC.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_10-001-0001_PR_REC_20-80_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \caption{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ distribution. Four different network models are used (each with an average degree around 10 and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100 ($10\times100$), a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100 ($10\times100$), each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. For each model two different filtering algorithms are compared to each other: the REC and the PR filtering algorithm. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}
\end{figure}

\subsection{Echo chambers}
\textbf{Starting conditions $\bm{P_0(0) = 0.5}$ and $\bm{P_1(0)=0.5}$}\\
\newline
\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{echo_chambers_no_stubb_50-50_REC.png}
    \caption{REC}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{echo_chambers_no_stubb_50-50_PR.png}
    \caption{PR}
  \end{subfigure}
  \caption{Distribution of the fraction of friends (nearest neighbors, nn) of node $i$ with the same opinion 1 at $t = 500$. The distribution is normalized by dividing for the same quantity computed at $t=0$. \textbf{(a)} Results for the REC method; \textbf{(b)} Results for the PR method. Four different network models are used, each with a total number of nodes $N = 10^3$ and an average degree around 10: The Erd\H{o}s-R\'{e}nyi model (ER) with $p = 0.01$; The stochastic block model (SBM) with 10 communities of size 100 ($10\times 100$), a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; The stochastic Watts-Strogatz model (SBM-WS) with 10 communities of size 100 ($10\times100$), each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$; The Watts-Strogatz model (WS) with $K = 10$, two slightly different values of the clustering coefficient are used ($\left<C\right> \sim 0.55$ and $\left<C\right> \sim 0.60$). The starting conditions are $P_0(0) = 0.5$ and $P_1(0) = 0.5$. Each plot is the average of $10^2$ independent simulations.}%more explanation?
\end{figure}
\newpage
\noindent
\textbf{Starting conditions $\bm{P_0(0) = 0.2}$ and $\bm{P_1(0)=0.8}$}\\
\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{echo_chambers_no_stubb_ER_001_20-80_PR_REC.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{echo_chambers_no_stubb_WS_10_006_20-80_PR_REC_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_10x100_01-0001_003-0008_50-50_PR_REC.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{echo_chambers_no_stubb_SBM-WS_10_001_0001_10x100_20-80_PR_REC_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \caption{Distribution of the fraction of friends (nearest neighbors, nn) of node $i$ with the same opinion 1 at $t = 500$. The distribution is normalized by dividing for the same quantity computed at $t=0$. Four different network models are used, each with a total number of nodes $N = 10^3$ and an average degree around 10: \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100 ($10\times100$), a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100 ($10\times100$), each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. For each model two different filtering algorithms are compared to each other: the REC and the PR filtering algorithm. The starting conditions are $P_0(0) = 0.2$ and $P_1(0) = 0.8$. Each plot is the average of $10^2$ independent simulations.}
\end{figure}
